Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-01-02 paper/paper.tex
20200102 19:11:10

\subsection{Classical Monte Carlo}
\textcolor{red}{A introduction to classical Monte Carlo. Left blank currently.}

@@

\section{Moment Direction-Exact Diagonalization Results}
\textcolor{red}{Exact diagonalization results of the moment direction for FM and stripe phases. Left blank currently.}

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig. \ref{fig:ModelDefinition}(c). The green dashed lines and solid circles mark the ordered moment direction determined for the classical states, see main text for details. (a)-(b) Probability maps for the FM states in the \emph{FM-A} and \emph{FM-C} phase, respectively. (c)-{f} Proability maps for the stripe states in the \emph{Stripe-A}, \emph{Stripe-B}, \emph{Stripe-C}, \emph{Stripe-D}, resepctively.}
     \label{fig:Proabilities}
\end{figure}

\section{Summary}
\textcolor{red}{Summary of our work. Left blank currently.}

\section{Acknowledgements}
\textcolor{red}{Acknowledgements. Left blank currently.}

>>>>

\subsection{Classical Monte Carlo}
\textcolor{red}{A introduction to classical Monte Carlo.  To be accomplished $\cdots \cdots$}

@@

\section{Moment Direction-Exact Diagonalization Results}
\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig. \ref{fig:ModelDefinition}(c). The green dashed lines and solid circles mark the ordered moment direction determined for the classical states, see main text for details. (a)-(b) Probability maps for the FM states in the \emph{FM-A} and \emph{FM-C} phase, respectively. (c)-{f} Proability maps for the stripe states in the \emph{Stripe-A}, \emph{Stripe-B}, \emph{Stripe-C}, \emph{Stripe-D}, resepctively.}
     \label{fig:Proabilities}
\end{figure}

Having map out the global phase diagram of the $J-K-\Gamma$ model, we now move to the moment direction of these FM and stripe phases which provides key characteristic to distinguish them. Since the cluster spin-coherent state is captured by only a single pair ($\theta$, $\phi$) for collinear phases (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2.$

\subsection{Moment direction of the FM phases}
For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction(i.e., \textit{x}, \textit{y}, \textit{z} direction). However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction. To extract the moment direction of the \emph{FM-A} and \emph{FM-C} phases, we construct the following cluster spin-coherent state
\begin{equation}
    |\Psi(\theta, \phi) \rangle = \bigotimes_{i=1}^N|\theta,\phi \rangle
\end{equation}
and calculate the probabilities $P(\theta, \phi)$ with varying $\theta$ and $\phi$. The resulting probability maps are shown in Fig. \ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b).

\textcolor{red}{Moment direction of the FM phases. To be accomplished $\cdots \cdots$}

\subsection{Moment direction of the stripe phases}
\textcolor{red}{Moment direction of the stripe phases. To be accomplished $\cdots \cdots$}

\section{Summary}
\textcolor{red}{Summary of our work. To be accomplished $\cdots \cdots$}

\begin{acknowledgments}
    \textcolor{red}{Acknowledgements.  To be accomplished $\cdots \cdots$}
\end{acknowledgments}

% The following are the Appendixes of this article
\appendix

\section{Analysis of the classical energy and moment direction}

\textcolor{red}{Analysis of the classical energy and moment direction. To be accomplished $\cdots \cdots$}

\newpage
